---
title: "HW 2"
author: "Nicholas Marey"
date: "September 12, 2017"
output: pdf_document
---


#1. Assume the Bayesian model with likelihood Y | θ ∼ Binomial(n, θ) and prior θ ∼ Beta(a, b). Write a function that uses Monte Carlo sampling to estimate the posterior mean and standard deviation of θ given we observe Y = y. The function should take inputs y, n, a, and b. Given these inputs, the function should generate 1, 000, 000 samples of (θ, Y ) (by first drawing θ from a beta distribution and then Y | θ from a binomial distribution), extract the samples with Y = y, and return the mean and standard deviation of θ for these samples. Include code for this function in your write-up.

```{r}
question <- function(y, n, a, b){
  post<-matrix(0,nrow=1000000,ncol=length(y))
  for(i in y){
    post[,i]<-rbeta(1000000,y[i]+a,n-y[i]+b)
  }
  #post<-rbeta(1000000, y+a, n-y+b) #posterior probability distribution
  mean(post) #posterior mean
  sd(post) #posterior standard deviation
}


```

#2. Use the code from (1) with n = 10 and a = b = 1 to compute the posterior mean and standard deviation for θ for all y = 0, 1, . . . , n and plot the posterior mean and standard deviation as a function of y.


```{r }
set.seed(1)
p2<-question(y, 10, 1, 1)

```

#3. Use the code from (1) with n = 10 and a = b = 10 to compute the posterior mean and standarddeviation for θ for all y = 0, 1, . . . , n and plot the posterior mean and standard deviation as a function of y.


```{r }
set.seed(1)
p3<-question(0:10, 10, 10, 10)
```

# 4. Comment on the differences between the plots with a = b = 1 versus a = b = 10.

