---
title: "Homework 4  - Stat 488 Bayesian Analysis"
author: "Nicholas Marey"
date: "September 26, 2017"
output: pdf_document
---
#Question 1
**Say that $Y \sim Binomial(N, \theta)$, where $N \in \{0, 1, 2, . . .\}$ is the unknown parameter of interest and has prior $N \sim Poisson(1)$.**

## Part (a)
**Given $Y = 5$ and $\theta = 0.5$, plot the posterior distribution of $N$.**
```{r tidy=TRUE}
func<-function(N,Y,theta,lambda){
    choose(N,Y)*theta^N*(1-theta)^(N-Y)*((lambda^Y*exp(-lambda))/factorial(Y))
}

n<-5:20

plot(n,func(N=n,Y=5,theta=0.5,lambda=1),ylab="f(N| Y, theta)",xlab="N", main="Posterior Distribution of N")
```

## Part (b)
**Given $Y = 5$ and $\theta = 0.1$, plot the posterior distribution of $N$.**
```{r tidy=TRUE}
plot(n,func(N=n,Y=5,theta=0.1,lambda=1),ylab="f(N| Y, theta)",xlab="N", main="Posterior Distribution of N")
```

## Part (c)
We know the number of complete passes thrown by the Bears quarterback and want to determine the distribution of the total number of passes attempted. 

#Question 2
**A clinical trial was conducted to compare the effectiveness of three drugs. 100 patients were randomly assigned to each drug (300 total patients), and $Y_1 = 12$, $Y_2 = 18$, and $Y_3 = 10$ patients had successful outcomes in the three drug groups. Using uniform priors for the success probabilities of each drug:**


##Part (a)
**Compute and plot the posterior distribution of the success probability for each drug.**

*Likelihood*
$$Y_1, Y_2, Y_3 | \theta  \sim Binomial(n,\theta)$$
$$f(y_1, y_2, y_3 | \theta) = {{n}\choose{y_i}} (\theta)^{y_i}(1-\theta)^{n-y_i}$$
*Prior Distribution*
$$\theta \sim Beta(a,b)$$
$$f(\theta) = \frac{(a+b)}{(a)(b)}\theta^{a-1}(1-\theta)^{b-1}$$

*Posterior Distribution*
$$\theta | y \sim Beta(y+a, n-y+b)$$







```{r tidy=TRUE}
plot(seq(0,1,length=100),dbeta(seq(0,1,length=100),12+1,100-12+1),
     type="l",col="red",
     ylim=c(0,14), 
     ylab = "Density", 
     xlab="N", 
     main = "Drug Analysis")
lines(seq(0,1,length=100),dbeta(seq(0,1,length=100),18+1,100-18+1),col="blue")
lines(seq(0,1,length=100),dbeta(seq(0,1,length=100),10+1,100-10+1),col="green")
legend("topright", legend=c("=Y1","=Y2","=Y3"),lty=c(1,1,1),col=c("red","blue","green"))

```

##Part (b)
**Compute the posterior probability that drug 2 is the best drug.**
```{r tidy=TRUE}
set.seed(1)

drug1<-rbeta(1e6,12+1,100-12+1)
drug2<-rbeta(1e6,18+1,100-18+1)
drug3<-rbeta(1e6,10+1,100-10+1)

mean(drug2 > drug1 | drug2>drug3)

```
The posterior probability that drug 2 is the best drug is 0.987229




