---
title: "Homework 4  - Stat 488 Bayesian Analysis"
author: "Nicholas Marey"
date: "September 26, 2017"
output: pdf_document
---
#Question 1
**Say that $Y \sim Binomial(N, \theta)$, where $N \in \{0, 1, 2, . . .\}$ is the unknown parameter of interest and has prior $N \sim Poisson(1)$.**

## Part (a)
**Given $Y = 5$ and $\theta = 0.5$, plot the posterior distribution of $N$.**
```{r }
func<-function(N,Y,theta){
    choose(N,Y)*theta^N*(1/(exp(1)*factorial(Y)))
}

n<-5:100

plot(n,func(n,5,0.5))
```

## Part (b)
**Given $Y = 5$ and $\theta = 0.1$, plot the posterior distribution of $N$.**
```{r}

plot(n,func(n,5,0.1))
```

## Part (c)
sitting on a street corner and count the number of bicycles per hour and count the other cars per hour that pass by. 

#Question 2
**A clinical trial was conducted to compare the effectiveness of three drugs. 100 patients were randomly assigned to each drug (300 total patients), and $Y_1 = 12$, $Y_2 = 18$, and $Y_3 = 10$ patients had successful outcomes in the three drug groups. Using uniform priors for the success probabilities of each drug:**

Uniform prior with binomial likelihood?
##Part (a)
**Compute and plot the posterior distribution of the success probability for each drug.**
```{r}

```

##Part (b)
**Compute the posterior probability that drug 2 is the best drug.**
```{r}

```

