---
title: "Bayesian HW 5"
author: "Nicholas Marey"
date: "November 14, 2017"
output: pdf_document
---

Download the data. 

```{r}
load(url("http://math.luc.edu/~ebalderama/bayes_resources/data/Homes.RData"))
ls()
```


Let $Y_i$ be the precipitation for observation $i$ and let $X_{ij}$ equal one if OTU $j$ present in sample $i$.


```{r}
Y <- homes[, "MeanAnnualPrecipitation"]
X <- ifelse(OTU > 0, 1, 0)
n <- nrow(X)
dim(X)
```

Extract the 50 OTU with the largest absolute correlation between $X_{ij}$ and $Y_i$.

```{r}
p <- 50
corr <- abs(cor(Y, X))
index <- order(corr, decreasing = TRUE)[1:p]
X <- X[,index]
dim(X)
```

Now fit a Bayesian linear regression model in Stan with precipitation as the response against these 50 covariates (and an intercept term) using three priors:

1. Uninformative Normal Priors: $\beta_j \sim \text{Normal}(0,100)$.

2. Hierarchical Normal Priors: $\beta_j | \tau \sim \text{Normal}(0,\tau) $, where $\tau^2 \sim \text{InerseGamma}(0.01, 0.01)$. tau^2 not same as tau

3. Bayesian LASSO: $\beta_j | \tau \sim \text{DE}(0,\tau)$, where $\tau^2 \sim \text{InverseGamma}(0.01,0.01)$. tau^2 follows Double exponential pg 528

##Uninformative Normal Priors
```{r}
data {
int<lower=0> N;
vector[N] x;
vector[N] y;
}
parameters {
real alpha;
real beta;
real<lower=0> sigma;
}
model {
y ~ normal(alpha + beta * x, sigma);
}
```


##Hierarchial Normal Priors
```{r}

```

##Bayesian LASSO
```{r}

```

Notes:
should get a beta for each of the 50 coloumns, an intercept term, a sigma term.
Could give the sigma flat priors?
QR reparameteriziation is more eficient. decomposing X matrix into orthogonal matrix Q and upper triangular matrix R (page 125 in manual). 











